\section{Technologies and Architecture}

Before implementing a specific functionality of the system, each component of the system needs to be setup and configured, so that an iterative development process can be done correctly. For certain components of the system, a live environment is configured, so that the system is accessible via a public URL, without having to set it up locally. 

\subsection{Prerequisites}

  There are certain prerequisites before setting up the projects locally. The prerequisites that need to be met are: 

  \begin{itemize}
  \item Node.JS version 16 is installed
  \item NPM is installed
  \item Docker is installed
  \item Git is installed
  \end{itemize}

 \subsection{User Interface}

    As mentioned in \autoref{concept_ui}, the UI is a web application, built using Vue3 and TypeScript. The subsection describes how to set up the UI project locally and explains some technical details of the UI project. 

  \subsubsection{Setup}
   Nowadays, most front end projects use some kind of build tool to help build, test, and develop web applications\footnote{For detailed information on the role of a build tool in front end development, please take a look at \autocite{Odell2014}.}. \emph{Vite}\footnote{\emph{Vite} is an open source front end build tool. GitHub repository: \url{https://github.com/vitejs/vite}.} is used as the build tool for the UI project. A new Vite project is created by running the following command in a shell terminal:
  
  \begin{lstlisting}[caption={Creating a new Vite project (Shell)}]
 npm create vite@latest ui --template vue-ts
  \end{lstlisting}

  A version control to track and manage the progress done in this particular project is also used. The version control used in this project is git and a code hosting platform for version control is also used for the project (GitHub).

  \subsubsection{Component Library}
  A component library is used in this project to speed up the development of the UI. The component library used in this project is \emph{NaiveUI}\footnote{\emph{NaiveUI} is a Vue3 component library. GitHub repository: \url{https://github.com/TuSimple/naive-ui}.}. NaiveUI is chosen because it contains several components that are suitable for the project (for example: \verb;Timeline;, \verb;Menu;) and it also supports TypeScript out of the box.

  \subsubsection{Code Style}
  To enforce a consistent code style and comply to the best practices of a TypeScript project, a code formatter (\emph{Prettier}) and linter (\emph{ESLint}) are used in this project. 

  \subsubsection{Docker}
  The UI can also run as a Docker container. Below is the \verb;Dockerfile; implementation for the UI project. 

  \begin{lstlisting}[caption={Dockerfile for FDS (Docker)}, language=docker]
FROM node:16-alpine

RUN npm install -g http-server
WORKDIR /app

COPY package*.json ./

RUN npm install
COPY . .

RUN npm run build

EXPOSE 3000
CMD [ "http-server", "dist", "-p 3000"]
      \end{lstlisting}

  \subsubsection{CI/CD}
  A CI/CD process is configured within the project, to run certain actions on specific events that happen in the codebase. The tool used as a CI/CD platform is \emph{GitHub actions}\footnote{\emph{GitHub actions} is a CI/CD platform, created by GitHub and can be used in all repositories hosted on GitHub. Homepage: \url{https://github.com/features/actions}.}. The configured CI/CD actions in this project are:

   \begin{itemize}
    \item Run test and build, when there's a new pull request (PR)\footnote{\emph{Pull request (PR)} is a request from a developer to merge certain changes on a dedicated branch to the main branch of a repository.} to \verb;main; branch
    \item Run release and increase the version of the app, when there's a new commit to \verb;main; branch
   \end{itemize}
  
  \subsubsection{Deployment}
  A live environment is available for the UI, made possible by using \emph{Netlify}\footnote{\emph{Netlify} is a hosting platform with a git-based workflow. Homepage: \url{https://www.netlify.com/}.}. Every change made to the \verb;main; branch will be built and deployed on the Netlify platform automatically. 

 \subsection{FDS}
 As described in \autoref{concept_fds}, the FDS is a server side application, built with Node.JS and TypeScript. To build a REST API with ease, the Express.JS framework will also be used in this project. This subsection describes the setup and other technical details revolving the FDS project. 

  \subsubsection{Setup}
  To set up a new Node.JS project, run the following command in a shell terminal:

   \begin{lstlisting}[caption={Creating a new Node.JS program (Shell)}]
 mkdir fds
 cd ./fds
 npm init -y
   \end{lstlisting}
   
  To use the TypeScript language rather than plain JavaScript, the TypeScript compiler needs to be installed and used in this project. The TypeScript compiler can also be configured to be more suitable to the personal preferences of the developer as well as the requirements of third party libraries used by the project. To install TypeScript as a development dependency\footnote{In a Node.JS project, development dependency is a third party library used only for development purposes.} and to generate a configuration file for the TypeScript compiler, run the following commands in a shell terminal:
  
   \begin{lstlisting}[caption={Installing and configuring TypeScript compiler (Shell)}]
 npm i -D typescript
 tsc --init
   \end{lstlisting}
  
  To install Express.JS in the current project, run the following command in a shell terminal:
  
   \begin{lstlisting}[caption={Installing Express.JS (Shell)}]
 npm i express
   \end{lstlisting}
  
  \subsubsection{Database Connection with ORM (Prisma)}
   To set up a database connection with Prisma (the ORM library of choice for FDS), the Prisma package should be installed in the current project by running the following command in a shell terminal:

   \begin{lstlisting}[caption={Installing Prisma (Shell)}]
 npm i -D prisma 
 npm i @prisma/client
   \end{lstlisting}

   After installing the Prisma package, set up the current project to work with Prisma ORM by running the following command in a shell terminal:

   \begin{lstlisting}[caption={Set up project with Prisma}]
 npx prisma init
   \end{lstlisting}
   
   After the project is set up, a \verb;prisma.schema; file will be created. The \verb;prisma.schema; file is used as a configuration file for the Prisma client and to define the database schema. The type of the database system as well as its URL should be configured in this \verb;prisma.schema; file. 

   \begin{lstlisting}[caption={Configuring database type and URL (Prisma)}]
 datasource db {
   provider = "mongodb"
   url      = env("DB_URL")
 }  
   \end{lstlisting}

   In this particular example, the database system for the current project is set to MongoDB, and the database URL will be set by the \verb;DB_URL; environment variable.

   As the configuration is done and the database schema is created, the Prisma client API has to be updated to include the interfaces generated from the schema by running \verb;npx prisma generate;.
   
  \subsubsection{Tsoa and Swagger}
  Even though Express.JS provides a declarative and easy way to build a server side application, it's built for a JavaScript application. Although TypeScript can be used with Express.JS, it doesn't use all the potential functionalities that TypeScript provides. \emph{Tsoa}\footnote{\emph{Tsoa} GitHub repository: \url{https://github.com/lukeautry/tsoa}.} is a framework with integrated openAPI compiler to build server side applications that can leverage TypeScript to its potential. Tsoa helps an express application to have the following functionalities out of the box:

   \begin{itemize}
    \item Generate Swagger\footnote{\emph{Swagger} is a tool to document server side APIs. Homepage: \url{https://swagger.io/}.} specification based on HTTP controller code
    \item Generate Swagger schema based on TypeScript interfaces
    \item Generate Swagger schema descriptions based on \emph{jsDoc}\footnote{\emph{jsDoc} is a tool to generate API documentation, similar to \emph{JavaDoc}. Homepage: \url{https://jsdoc.app/}.} comments on the source code
    \item Validates an HTTP request body based on TypeScript interfaces
   \end{itemize}
  
  Tsoa provides an alternative syntax to build an Express.JS application in a more object-oriented way. Tsoa works by compiling the code, using the TypeScript and openAPI compiler into a regular Express.JS application. 

  \subsubsection{Code Style}
  Identical to the UI project, a code formatter (\emph{Prettier}) and linter (\emph{ESLint}) are also used in this project. The configuration for the code formatter and linter is slightly different in comparison to the UI project, as certain code style rules doesn't apply to a server side application\footnote{In the UI project, there are certain code style rules regarding HTML elements.}.

  \subsubsection{Docker}
  The application will be built and run as a Docker container. A \verb;Dockerfile; is provided, containing a list of commands needed to be run to assemble the particular image.

   \begin{lstlisting}[caption={Dockerfile for FDS (Docker)}, language=docker]
 FROM node:16-alpine

 ARG ARG_1 # Arguments passed by --build-args flag
 ENV ARG_1=$ARG_1 # Environment variable of the image

 WORKDIR /app
 COPY ["package.json", "package-lock.json*", "./"]

 RUN npm ci # Install packages
 COPY . .
 # Additional steps to setup the application

 RUN npm run build
 ENV NODE_ENV=production

 CMD [ "node", "./dist/src/main.js" ]
   \end{lstlisting}
  
  \subsubsection{CI/CD}
  A CI/CD process is also configured for this project using GitHub actions. The actions configured in this project are:

   \begin{itemize}
    \item Run test and build, when there's a new PR to the \verb;main; branch
    \item Run release, bump version of the application and deploy it to the live environment, when there's a new commit to \verb;main; branch
   \end{itemize}
   
  \subsubsection{Deployment}
  A live environment is available for the FDS application. The FDS is deployed and run as a Docker container in \emph{Heroku}\footnote{\emph{Heroku} is a platform as a service (PaaS) that provides a platform for developer to build and run application in the cloud. Homepage: \url{https://heroku.com}.}. The deployment process will be executed via the CI/CD action on every commit to the \verb;main; branch. 

 \subsection{RabbitMQ}
 A RabbitMQ instance is required as one of the integral parts of the system. Fortunately, RabbitMQ provided an official Docker image for it and running a RabbitMQ instance as a Docker container is as simple as running the following command in a shell terminal:

 \begin{lstlisting}[caption={Running a RabbitMQ instance with Docker (Shell)}]
 docker run -it --rm --name rabbitmq -p 5672:5672 -p 15672:15672 rabbitmq:3.10-management 
 \end{lstlisting}

 The command listed above will locally run the RabbitMQ instance on port \verb;5672; and the RabbitMQ management UI on port \verb;15672;. On the live environment, a service called \emph{CloudAMQP}\footnote{\emph{CloudAMQP} is a service provider (RabbitMQ as a Service) that offers RabbitMQ clusters setup and management.} is used to help in setting up a RabbitMQ instance in the cloud, so that it can be accessed by other components via its public URI easily.

 \subsection{Redis}
 Redis is used in the system as a caching memory and a temporary data store. Redis also provided an official Docker image. To run a Redis instance as a Docker container, the following command should be run in a shell terminal:

 \begin{lstlisting}[caption={Running a Redis instance with Docker (Shell)}]
 docker run -d --name redis-stack-server -p 6379:6379 redis/redis-stack-server:latest
 \end{lstlisting}

 The command listed above will locally run the Redis instance on port \verb;6379;. Redis is not available on the live environment. Therefore, no caching is available and an in memory data store (a basic JavaScript class) is used to replace Redis as the temporary data store.

 \subsection{MongoDB}
 MongoDB is the database of choice for the system. MongoDB has an official Docker image and the following command should be run in a shell terminal to set up a MongoDB instance locally:

 \begin{lstlisting}[caption={Running a MongoDB instance with Docker (Shell)}]
 docker run --name mongodb -d -p 27017:27017 mongo 
 \end{lstlisting}

 By running the command listed above, a MongoDB instance will be run locally on port \verb;27017;. On the live environment, a service called \emph{MongoDB Atlas}\footnote{\emph{MongoDB Atlas} is a service that provides a cloud-hosted MongoDB instances. Homepage: \url{https://www.mongodb.com/atlas}.} will be used to help host a MongoDB instance in the cloud, making it more accessible by other components of the system.
 
  % Add info on creating user, connecting to shell, creating database
  % docker exec -it mongodb mongosh
  % use fds;
  % use admin; db.createUser({ user: "admin", pwd: "admin", roles: [{role: "dbAdmin" , db:"fds"}] }a)

 \subsection{Docker Compose}

    Docker Compose is used to as a tool to start and set up the components of the system as Docker containers using a single \verb;docker-compose up -d; command. To use Docker Compose, a configuration file is needed in a directory that contains the FDS and the UI project\footnote{Docker Compose configuration file is listed on \autoref{code:compose}.}.
    
    The environment variables of the FDS, such as the database URI and the RabbitMQ URI can be configured from the Docker Compose configuration file, making it easier to configure the current context of the system without having to introduce any change to the existing code base. 
    
    \begin{lstlisting}[caption={Configuring environment variables of FDS (YAML)}, language=yaml]
environment:
  - ENABLE_CACHE: true
  - DATA_STORE: "redis"
  - DATABASE_URL: "mongodb://root:prisma@mongo:27018/tests?authSource=admin/"
  - REDIS: "redis://redis:6379/"
  - RABBITMQ_URL: "amqp://rabbit:5672"
  - RABBITMQ_MANAGEMENT_UI: "http://rabbit:15672"
    \end{lstlisting}
    
    Running all the components of the system using a single command as Docker containers is useful, because it provides a solution on the added complexity of installing the needed dependencies and running each component individually. 

    Unfortunately, even though each component of the system is started by using the \verb;docker-compose up -d; command, doesn't mean that every component is ready to be used directly. The RabbitMQ component needs a while to boot up, and therefore the FDS cannot yet be started until RabbitMQ is ready to accept any ongoing connection. Therefore, an additional function is implemented on the FDS to make sure that RabbitMQ is ready before attempting to connect, by waiting for the RabbitMQ management UI\footnote{The RabbitMQ management UI is available via a RabbitMQ plugin, also provided by the official Docker image.} to respond in a given time period.